### 2024-03-15 sections/1stratified.tex

\begin{definition}
    Given a $C^0$ stratified space $(X \xrightarrow{s} P)$ the \emph{depth at $x$} is
    %
    \begin{equation}
        \mathsf{dpt}_x (X) := \mathsf{dim}_x (X) - \mathsf{dim}_x (X_{s(x)}).
    \end{equation}
    %
    The depth of $X$, $\mathsf{dpt} (X)$, in general is the supremum of the depths over all points. Just as with dimension, the convention is that $\mathsf{dpt}(\emptyset) = -1$.
\end{definition}

@@

\begin{definition}
    Given an $\infty$-category of basics $\bstr \rightarrow \bsc$, the $\infty$-category of $\bstr$-manifolds is the pullback
    %
    \begin{equation}
        \begin{tikzcd}
            \mfld(\bstr) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & (\mathsf{RFib}_{\bsc})_{/\bstr} \arrow[d] \\
            \mfld \arrow[r, "\tau"] & \mathsf{RFib}_{\bsc}
        \end{tikzcd}
    \end{equation}
    where we abbreviated $(\bstr\to\bsc)\in\mathsf{RFib}_{\bsc}$ to $\bstr$. Similarly the ordinary category $\mfld[r](\bstr)$ of $\bstr$-manifolds is the further pullback along the inclusion $\mfld[r]\to\mfld$.
\end{definition}

@@

\begin{remark}
    \Cref{thm:decom_strat_man} is the analogue of handle decompositions for smooth manifolds. Namely, any compact, smooth manifold can be obtained by handle decomposition, and non-compact smooth manifolds are obtained by sequential colimits of finitary (including compact) smooth manifolds.
\end{remark}

@@

\begin{remark}
    Insisting that tangential structures be \emph{right fibrations} over $\bsc$, as opposed to simply $\infty$-categories over it as, e.g., in \cite{ayala2020factorization}, leads to technical issues that lead to our over-simplified notation due to the property of being a right fibration not being invariant under equivalence. For instance, when $G=\ast$, so that $\mathsf{D}^\ast_n$ constrols framed $n$-manifolds, the map $BG=\ast\to \mathsf{BO}(n)\simeq\mathsf{D}_n$ is not a right fibration, owing to the observation that right fibrations of Kan complexes are Kan fibrations, and these, when surjective on objects, are epimorphisms. On the other hand, $B\ast=\ast\simeq (\mathsf{D}_n)_{/\mathbb{R}^n}$ since over-$\infty$-groupoids are contractible (\cite[018Y]{lurie_kerodon}), but $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \mathsf{D}_n$ \emph{is} a right fibration since it is a projection from an over-$\infty$-category (\cite[018F]{lurie_kerodon}, \cite{joyal}). Moreover, $\mathsf{D}_n\hookrightarrow \bsc$ is a right fibration since this full $\infty$-subcategory is trivially a sieve, so the composition $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \bsc$ is a right fibration as well. In general, the map $\mathsf{B}G\to \mathsf{BO}(n)$ is not a right fibration unless $G\to\mathsf{O}(n)$ is an epimorphism. However, given the latter, we can consider the presheaf $\mathsf{D}_n^{\text{op}}\to\mathsf{Spaces}$ given by mapping $\mathbb{R}^n$ to the space of $G$-structures on it, and sending an embedding to the induced pullback map on the respective spaces of $G$-structures. By unstraightening, this determines a right fibration for which, by abuse, we write $\mathsf{D}^G_n=\mathsf{B}G\to \mathsf{D}_n\hookrightarrow\bsc$.
\end{remark}

>>>>

\begin{definition}
    Given a $C^0$ stratified space $(X \xrightarrow{s} P)$ the \emph{depth at $x$} is
    %
    \begin{equation}
        \mathsf{dpt}_x (X) := \mathsf{dim}_x (X) - \mathsf{dim}_x (X_{s(x)}).
    \end{equation}
    %
    The depth of $X$, $\mathsf{dpt} (X)$, in general, is the supremum of the depths over all points. Just as with dimension, the convention is that $\mathsf{dpt}(\emptyset) = -1$.
\end{definition}

@@

\begin{definition}
    Given an $\infty$-category of basics $\bstr \rightarrow \bsc$, the $\infty$-category of $\bstr$-manifolds is the pullback
    %
    \begin{equation}
        \begin{tikzcd}
            \mfld(\bstr) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & (\mathsf{RFib}_{\bsc})_{/\bstr} \arrow[d] \\
            \mfld \arrow[r, "\tau"] & \mathsf{RFib}_{\bsc}
        \end{tikzcd}
    \end{equation}
    where we abbreviated $(\bstr\to\bsc)\in\mathsf{RFib}_{\bsc}$ to $\bstr$. Similarly, the ordinary category $\mfld[r](\bstr)$ of $\bstr$-manifolds is the further pullback along the inclusion $\mfld[r]\to\mfld$.
\end{definition}

@@

\begin{remark}
    \Cref{thm:decom_strat_man} is the analogue of handle decomposition for smooth manifolds. Namely, any compact, smooth manifold can be obtained by handle decomposition, and non-compact smooth manifolds are obtained by sequential colimits of finitary (including compact) smooth manifolds.
\end{remark}

@@

\begin{remark}
    Insisting that tangential structures be \emph{right fibrations} over $\bsc$, as opposed to simply $\infty$-categories over it as, e.g., in \cite{ayala2020factorization}, leads to technical issues that lead to our over-simplified notation due to the property of being a right fibration not being invariant under equivalence. For instance, when $G=\ast$, so that $\mathsf{D}^\ast_n$ controls framed $n$-manifolds, the map $BG=\ast\to \mathsf{BO}(n)\simeq\mathsf{D}_n$ is not a right fibration, owing to the observation that right fibrations of Kan complexes are Kan fibrations, and these, when surjective on objects, are epimorphisms. On the other hand, $B\ast=\ast\simeq (\mathsf{D}_n)_{/\mathbb{R}^n}$ since over-$\infty$-groupoids are contractible (\cite[\href{https://kerodon.net/tag/018Y}{018Y}]{lurie_kerodon}), but $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \mathsf{D}_n$ \emph{is} a right fibration since it is a projection from an over-$\infty$-category (\cite[\href{https://kerodon.net/tag/018F}{018F}]{lurie_kerodon}, \cite{joyal}). Moreover, $\mathsf{D}_n\hookrightarrow \bsc$ is a right fibration since this full $\infty$-subcategory is trivially a sieve, so the composition $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \bsc$ is a right fibration as well. In general, the map $\mathsf{B}G\to \mathsf{BO}(n)$ is not a right fibration unless $G\to\mathsf{O}(n)$ is an epimorphism. However, given the latter, we can consider the presheaf $\mathsf{D}_n^{\text{op}}\to\mathsf{Spaces}$ given by mapping $\mathbb{R}^n$ to the space of $G$-structures on it, and sending an embedding to the induced pullback map on the respective spaces of $G$-structures. By unstraightening, this determines a right fibration for which, by abuse, we write $\mathsf{D}^G_n=\mathsf{B}G\to \mathsf{D}_n\hookrightarrow\bsc$.
\end{remark}
